---
title: "R Assignment 1"
author: "Daina Bouquin"
date: "July 4, 2015"
output: html_document
---

First R assignment for my MS in Data Analytics Summer R Refresher course.

1. Write a loop that calculates 12-factorial.
```{r, echo=TRUE}

x <- 12
y <- 1

for(i in 1:x){
    y <-y*((1:x)[i])
}
y

#check with factorial()

y == factorial(12)

```
2. Show how to create a numeric vector that contains the sequence from 20 to 50 by 5.
```{r, echo=TRUE}

seq_1 <- seq(from=20, to=50, by=5)
seq_1

```
3. Show how to take a trio of input numbers a, b, and c and implement the quadratic equation.

This below response is built from an online example I found on [the R Help Mailing List](https://stat.ethz.ch/pipermail/r-help/2005-November/082164.html) by Ted Harding.

Couldn't it be more efficient to use polyroot?

```{r, echo=TRUE}

# ax2 + bx + c = 0

a <- 1
b <- 4
c <- 3

qs <- function(a,b,c){
    a <- as.complex(a); b <- as.complex(b); c <- as.complex(c)
    i2 <- (a!=0); i1 <- ((a==0)&(b!=0));
    solns <- as.complex(rep(NA,length(a)))
      solns <- cbind(solns,solns); colnames(solns) <- c("solution1","solution2")
    a2 <- a[i2]; b2 <- b[i2]; c2 <- c[i2]
      solns[i2,1] <- (-b2 + sqrt(b2^2 - 4*a2*c2))/(2*a2)
      solns[i2,2] <- (-b2 - sqrt(b2^2 - 4*a2*c2))/(2*a2)
    b1 <- b[i1]; c1 <- c[i1]
      solns[i1,1] <- (-c1)/b1
    solns
  }

qs(a,b,c)

```

